### 2023-03-16 paper/fse23/tables/test-results-hs-table.tex
icse24

\multirow{2}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-hs-lc0}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc0-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc0-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc0-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc0-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc0-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc0-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc0-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc0-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc0-num-pass-to-fail}\\
\multirow{2}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-hs-lc1}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc1-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc1-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc1-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc1-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc1-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc1-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc1-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc1-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc1-num-pass-to-fail}\\
\multirow{2}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-hs-lc2}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc2-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc2-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc2-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc2-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc2-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc2-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc2-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc2-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc2-num-pass-to-fail}\\
\multirow{2}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-hs-lc3}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc3-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc3-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc3-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc3-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc3-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc3-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc3-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc3-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc3-num-pass-to-fail}\\
\multirow{2}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-hs-lc4}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc4-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc4-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc4-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc4-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc4-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc4-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc4-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc4-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc4-num-pass-to-fail}\\
\multirow{2}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-hs-lc5}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc5-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc5-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc5-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc5-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc5-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc5-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc5-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc5-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc5-num-pass-to-fail}\\
\multirow{2}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-hs-lc6}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-hs-lc7}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-hs-lc8}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-hs-lc9}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC11: \UseMacro{test-results-hs-lc10}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC12: \UseMacro{test-results-hs-lc11}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC13: \UseMacro{test-results-hs-lc12}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC14: \UseMacro{test-results-hs-lc13}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC15: \UseMacro{test-results-hs-lc14}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC16: \UseMacro{test-results-hs-lc15}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC17: \UseMacro{test-results-hs-lc16}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC18: \UseMacro{test-results-hs-lc17}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC19: \UseMacro{test-results-hs-lc18}}}

@@

>>>>

\multirow{2}{*}{\parbox{8cm}{LC1: \UseMacro{test-results-hs-lc6}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC2: \UseMacro{test-results-hs-lc7}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC3: \UseMacro{test-results-hs-lc8}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC4: \UseMacro{test-results-hs-lc9}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC5: \UseMacro{test-results-hs-lc10}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC6: \UseMacro{test-results-hs-lc11}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC7: \UseMacro{test-results-hs-lc12}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC8: \UseMacro{test-results-hs-lc13}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC9: \UseMacro{test-results-hs-lc14}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC10: \UseMacro{test-results-hs-lc15}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC11: \UseMacro{test-results-hs-lc16}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC12: \UseMacro{test-results-hs-lc17}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC13: \UseMacro{test-results-hs-lc18}}}

@@

\multirow{2}{*}{\parbox{8cm}{LC14: \UseMacro{test-results-hs-lc19}}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-bl-lc19-num-tcs}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc19-num-seeds}}
 & \multirow{2}{*}{\centering\UseMacro{test-results-hs-lc19-num-exps}}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc19-num-all-fail}/\UseMacro{test-results-hs-bl-model0-lc19-num-fail}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc19-num-all-failrate}/\UseMacro{test-results-hs-bl-model0-lc19-num-failrate}
 & alex-BERT$\colon$\UseMacro{test-results-hs-model0-lc19-num-pass-to-fail}\\
 & & & & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc19-num-all-fail}/\UseMacro{test-results-hs-bl-model1-lc19-num-fail}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc19-num-all-failrate}/\UseMacro{test-results-hs-bl-model1-lc19-num-failrate}
 & CNERG-BERT$\colon$\UseMacro{test-results-hs-model1-lc19-num-pass-to-fail}\\

### 2023-03-16 paper/icse24/CM/coverage.tex
icse24

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/nlp_coverage.pdf}
    \vspace{-6mm}
    \caption{Coverage results of \tool and \Cklst test cases.}
    \label{fig:coverage}
\end{figure}

\paragraph*{Model Coverage} Figure \ref{fig:coverage} shows the coverage results of \tool and \Cklst test cases. The red line represents \tool coverage and the black line represents \Cklst coverage. Each column in Figure \ref{fig:coverage} represents the results for one NLP model. The first row is the \textit{BoundCov} results and the second row is the \textit{SActCov} results.

We made three observations.
First, for \emph{all} experimental settings (i.e., NLP model and coverage metric), \tool achieves higher coverage than \Cklst. Recall that a higher coverage implies the test cases are more diverse and do not have a similar statistical distribution to the model training data. As a result, a test suite with greater coverage complements the model training data distribution (\ie holdout testing data) better.
For example, for the first NLP model under test, \tool can achieve a higher coverage than \Cklst with only half the number of test cases.
This result confirms that \tool can generate more diverse test cases to complement the holdout dataset for testing NLP models.
Second, as the number of test cases increases, the test suite can achieve better coverage. Such observation is intuitive. However, generating a more extensive test suite is not easy, particularly  for \Cklst, which is a manually template-based approach.
Third, for each NLP model, there is no fixed relationship between \textit{BoundCov} and \textit{SActCov}. In other words, while a test suite may produce higher \textit{BoundCov} for some models, the same test suite may get higher \textit{SActCov} for other NLP models.
Recall that \textit{BoundCov} measures both the upper and lower corner neurons and \textit{SActCov} measures only the upper corner neurons. 
Such observation implies that the upper and lower corner neurons are distributed unevenly, and measuring only one of them is not enough.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/nlp_coverage.pdf}
    \vspace{-6mm}
    \caption{Coverage results of \tool and \Cklst.}
    \label{fig:coverage}
\end{figure}

\MyPara{Neuron Coverage} 
Figure \ref{fig:coverage} shows the coverage results of \tool and \Cklst test cases. The red line represents \tool coverage and the black line represents \Cklst coverage. Each column in Figure \ref{fig:coverage} represents the results for one \sa model. The first row is the \textit{BoundCov} results and the second row is the \textit{SActCov} results.
We made three observations from the results.
First, for \emph{all} experimental settings (i.e., NLP model and coverage metric), \tool achieves higher coverage than \Cklst. Recall that a higher coverage implies the test cases are more diverse and do not have a similar statistical distribution to the model training data. As a result, a test suite with greater coverage complements the model training data distribution (\ie holdout testing data) better.
For example, for the first NLP model under test, \tool can achieve a higher coverage than \Cklst with only half the number of test cases.
This result confirms that \tool can generate more diverse test cases to complement the holdout dataset for testing NLP models.
Second, as the number of test cases increases, the test suite can achieve better coverage. Such observation is intuitive. However, generating a more extensive test suite is not easy, particularly  for \Cklst, which is a manually template-based approach.
Third, for each NLP model, there is no fixed relationship between \textit{BoundCov} and \textit{SActCov}. In other words, while a test suite may produce higher \textit{BoundCov} for some models, the same test suite may get higher \textit{SActCov} for other NLP models.
Recall that \textit{BoundCov} measures both the upper and lower corner neurons and \textit{SActCov} measures only the upper corner neurons. 
Such observation implies that the upper and lower corner neurons are distributed unevenly, and measuring only one of them is not enough.

### 2023-03-16 paper/icse24/abstract_old.tex
icse24

\begin{abstract}
  \Nlp has been widely used for developing a variety of text analytic applications with high reliability. For any NLP-based applications to be trustworthy, assessment through measuring the accuracy of the holdout datasets is needed. Recent research introduced methods that assess an NLP model on a set of linguistic capabilities.
  However, we observe that state-of-the-art methods rely on manually created test cases, which may be limited in terms of scalability and diversity.
%\Nlp (NLP) technique has become one of the core techniques fordeveloping text  analytic applications.  These applications need to achieve high reliability to be useful in practice.  
%The trustworthiness of the NLP applications is often obtained by measuring the accuracy ofthe applications on holdout datasets. However, assessing an NLP application on the accuracy of the holdout datasets is limited in validating its overallquality because these datasets are often notcomprehensive. 
  %To address this limitation, methodologies to assess an NLP model on a set oflinguistic capabilities has recently been introduced. However, current state-of-the-art methodologies rely on manuallycreated test cases which limits the scale of the testing dataset. 
  In this work, we introduce \tool,
  an automated linguistic capability-based testing technique.  Given a set of linguistic capabilities that assess an NLP model, \tool first searches for suitable seed inputs from existing datasets, and then generates a sufficient number
  of new test inputs by expanding the seed inputs based on their \cfg (CFG). 
  \tool guarantees the correctness of the generated test input labels and that these test inputs belong to the correct linguistic capabilities. 
  Evaluation results show that \tool can generate test cases that are 100\%  more diverse than state-of-the-art 
   while ensuring the correctness of labels and linguistic capabilities of the test inputs. 
%   \Cong{You mention comprehensive and scalability before, so better give improvement numbers in terms of these metrics.}
  We also show that \tool facilitates the identification of critical failures and its origins in the NLP models.
\end{abstract}

>>>>

\begin{abstract}

\Nlp has been widely used for developing a variety of text analytic applications. 
For NLP-based applications to be trustworthy, %assessment through measuring the accuracy of the holdout datasets is needed. 
recent research introduced methods that assess an NLP model on a set of linguistic capabilities.
However, state-of-the-art methods rely on manually created test cases, which may be limited in terms of scalability and diversity.
%\Nlp (NLP) technique has become one of the core techniques fordeveloping text  analytic applications.  These applications need to achieve high reliability to be useful in practice.  
%The trustworthiness of the NLP applications is often obtained by measuring the accuracy ofthe applications on holdout datasets. However, assessing an NLP application on the accuracy of the holdout datasets is limited in validating its overallquality because these datasets are often notcomprehensive. 
%To address this limitation, methodologies to assess an NLP model on a set oflinguistic capabilities has recently been introduced. However, current state-of-the-art methodologies rely on manuallycreated test cases which limits the scale of the testing dataset. 
In this work, we introduce \tool, an automated linguistic capability-based testing technique. 
Given a set of linguistic capabilities that assess an NLP model, 
\tool first searches for suitable seed inputs from existing datasets, 
and then generates a sufficient number of new test inputs by expanding the seed inputs based on their \cfg (CFG).
\tool guarantees the correctness of the generated test input labels and that these test inputs belong to the correct linguistic capabilities. 
We evaluate \tool generated test cases on \lcs of \sa and \hsd tasks. Evaluation results show that \tool can generate test cases that are 100\% more diverse than \sota. In addition, while ensuring the correctness of labels and \lcs of the test inputs, 
\tool produces larger number of NLP model failures than \sota over 7 and 13 \lcs on all NLP models under test for \sa and \hsd tasks respectively. 
%   \Cong{You mention comprehensive and scalability before, so better give improvement numbers in terms of these metrics.}
We also show that \tool facilitates the identification of critical failures and its origins in the NLP models.
\end{abstract}
